---
title: "Data Visualization"
author: "Eduu"
date: "2024-09-11"
output: word_document
---

a)Creating a new column age.coded
```{r}
library(tidyverse)
library(mlbench)
data("PimaIndiansDiabetes")
PimaIndiansDiabetes<- PimaIndiansDiabetes %>% 
  mutate(Age.coded = cut(age,
                         breaks = c(20,25,30,35,40,45,50,100),
                         labels = c("20-25","26-30","31-35","36-40","41-45","46-50","51+"),
                         right = TRUE))
```

b)Bar chart of age.coded and diabetes
```{r}
PimaIndiansDiabetes %>%
  ggplot(aes(Age.coded,fill = factor(diabetes)))+
  geom_bar(position = "dodge")+
  labs(x = "Age group",
       y = "Diabetes Status across age groups",
       title = "Distribution of Diabetes status across Age groups")+
  theme_bw()
```

Findings:
Older age groups appear to have a higher count of diabetes-positive individuals compared to younger groups.
The age group "46-50+" shows a higher concentration of diabetes-positive cases.

c)Histogram of pedigree
```{r}
PimaIndiansDiabetes %>% 
  ggplot(aes(pedigree))+
  geom_histogram(binwidth = 0.1,fill = "green",color = "black")+
  labs(x = "Pedigree",
       y = "Frequency",
       title = "Histogram of Diabetes pedigree function")+
  theme_bw()
```
Finding:
Most individuals have a pedigree value between 0.0 and 0.4, indicating a relatively low genetic risk of diabetes.

d)Removing zeros in the glucose column and ploting a box plot
```{r}
PimaIndiansDiabetes %>% 
  filter(glucose > 0) %>% 
  ggplot(aes(Age.coded,glucose))+
  geom_boxplot()+
  labs(x = "Age groups",
       y = "Glucose levels",
       title = "Box plot of glucose levels across age groups")+
  theme_bw()
  
```
Finding:
Glucose levels tend to be higher in older age groups. However, younger groups show wider variability in glucose levels.
